Certified Knowledge Compilation \\ with Application to Formally Verified Model Counting

### 2024-01-06 doc/JAIR/jair-paper.tex
Change equivalence statement

Let $\exvarset(\theta)$
denote the set of extension variables occuring in formula $\theta$.
For any total assignment $\assign$ to the variables in $\varset$, the defining
clauses induce a unique assignment $\eassign$ to the variables in $\varset
\cup \exvarset(\theta)$.  For Boolean formula $\phi$ over variables
$\varset$ and clausal
formula $\theta$ over the variables $\varset \cup \exvarset(\theta)$, we say that $\phi$ is {\em
  effectively equivalent} to $\theta$, written
$\phi \eequiv \theta$,
when for any assignment
$\assign$ to the variables in $\varset$, assignment $\assign$ is a model of $\phi$ if
and only if its extension $\eassign$ is a model of $\theta$.
Starting with  $\theta$ equal to input formula $\inputformula$,
the proof must maintain the invariant that
$\inputformula \eequiv \theta$.

>>>>

Let $\exvarset(\theta)$
denote the set of extension variables occuring in formula $\theta$.
For any total assignment $\assign$ to the variables in $\varset$, the defining
clauses induce a unique assignment $\eassign$ to the variables in $\varset
\cup \exvarset(\theta)$.  For Boolean formula $\phi$ over variables
$\varset$ and clausal
formula $\theta$ over the variables $\varset \cup \exvarset(\theta)$, we say that $\phi$ is {\em
  equivalent over $\varset$} to $\theta$, written
$\phi \eequiv \theta$,
when for any assignment
$\assign$ to the variables in $\varset$, assignment $\assign$ is a model of $\phi$ if
and only if its extension $\eassign$ is a model of $\theta$.
Starting with  $\theta$ equal to input formula $\inputformula$,
the proof must maintain the invariant that
$\inputformula \eequiv \theta$.
